Array

### 2013-12-03 PAPERS/Report/AdvancedTypes/AdvancedTypes.tex
Added the rules to support array and the Node Lvalue.

\subsubsection{Issues and problems}
\begin{itemize}
	\item To develop support to structures (more easy)
	\item To integrate it in translation.tex
	\item To develop support to copy all  of an advanced types
	\item To identify the rules that must be updated:

\end{itemize}

@@

>>>>

\paragraph{Restriction on array and structure:} It is not yet supported the 
translation of direct attribution between array expression, for example:

\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
 array := array2;
 structure1 := structure2;
\end{minted}

\subsubsection{Issues and problems}
\begin{itemize}
	\item To develop support to structures (more easy)
	\item To integrate it in translation.tex
\end{itemize}

@@

\subsection{Structure examples}

The following code example is defining a structure:

\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
Year : struct(
	Year_number : INT,
	Leap_year : BOOL,
	Number_of_days : (1..12) * (28..31),
	Weather : struct( Average_Temperature : (1..12) *  INT,
		Average_Rain : (1..12) * INT) )
\end{minted}

The following code declares a record example:

\begin{minted}[frame=single,bgcolor=bg,linenos=true]{pascal}
Year := rec(
	Year_number : 2013,
	Leap_year : TRUE,
	Number_of_days : (12,28),
	Weather : rec(  Average_Temperature : (5,8),
			Average_Rain : (5,10)))
\end{minted}

\subsection{Arrays examples}
